Twists of supersymmetric gauge theories

### 2020-01-15 paper.tex
continuing with 3d

\begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ is equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$. 
\end{thm}

@@

\section{Dimension 3}
The 3-dimensional $\mc N=k$ supersymmetry algebra has odd part $\Sigma \iso S \otimes W$, where $S$ is the 2-dimensional spinor representation of $\Spin(3) \iso \SU(2)$, and where $W$ is a $k$-dimensional vector space equipped with a bilinear pairing.  The maximal supersymmetric gauge theory has $\mc N=8$.  However, there are $\mc N=4$ super Yang-Mills theories for every choice $U$ of symplectic representation of the gauge group, and $\mc N=2$ super Yang-Mills theories for every choice $R$ of arbitrary representation of the gauge group.

@@

\vspace{-10pt}
\paragraph{Twisting data:}
In the $\mc N=2$ supersymmetry algebra there is a unique non-trivial orbit of square zero supercharges, with rank one.

\subsection{$\cN = 4$ Super Yang-Mills with Hypermultiplet Matter}

>>>>

\begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$, with classical moduli space $T^*[-1]\mr{Map}(\CC^2, R/\gg)$. 
\end{thm}

@@

\section{Dimension 3}
The 3-dimensional $\mc N=k$ supersymmetry algebra has odd part $\Sigma \iso S \otimes W$, where $S$ is the 2-dimensional spinor representation of $\Spin(3) \iso \SU(2)$, and where $W$ is a $k$-dimensional vector space equipped with a bilinear pairing.  The maximal supersymmetric gauge theory has $\mc N=8$.  However, there are $\mc N=4$ super Yang-Mills theories for every choice $U$ of symplectic representation of the gauge group, and $\mc N=2$ super Yang-Mills theories for every choice $R$ of arbitrary representation of the gauge group.  In dimension 3, much like we saw in dimensions 5 and 7, all twisted theories can be obtained by dimensional reduction from theories one dimension higher.

@@

\vspace{-10pt}
\paragraph{Twisting data:}
In the $\mc N=2$ supersymmetry algebra there is a unique non-trivial orbit of square zero supercharges, with rank one. \chris{todo, say something about $\ZZ$-gradings and twisting homomorphisms.}

\begin{thm} \label{3d_minimal_twist_thm}
The minimal twist of 3d $\cN=2$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=2$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to mixed $BF$ theory for the Lie algebra $\fg$ coupled to the mixed $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$. 
\end{thm}

\begin{proof}
This follows by dimensionally reducing the holomorphic twist of 4d $\mc N=1$ super Yang-Mills.  That is, we start with the result from Theorem \ref{4d_minimal_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to turn one of the complex directions into a real de Rham direction.
\end{proof}

\subsection{$\cN = 4$ Super Yang-Mills with Hypermultiplet Matter}
We will now consider 3d $\mc N=4$ theories, which arise by dimensional reduction from 4d $\mc N=2$ super Yang-Mills with gauge group $G$, coupled to a hypermultiplet valued in a symplectic representation $U$, or equivalently by dimensional reduction from 6d $\mc N=(1,0)$ super Yang-Mills coupled to a hypermultiplet.

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from section \ref{4d_1_section} to representations of the group $\mr O(3)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and three scalar fields $(\phi_1,\phi_2,\phi_3) \in \Omega^0(\RR^3; \gg \oplus \gg \oplus \gg)$.
 \item $U$-valued bosons: a pair of $W$-valued scalar fields $(\phi \otimes v,\phi' \otimes v') \in \Omega^0(\RR^3; (W \oplus W) \otimes U)$.
 \item $\gg$-valued fermions: a pair of $W$-valued spinors $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes \gg \otimes (W \oplus W))$.
 \item $U$-valued fermions:  a pair of spinors $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
\end{itemize}

\vspace{-10pt}
\paragraph{Twisting data:}
In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.  In addition to rank one square-zero supercharges, which sit inside an $\mc N=2$ subalgebra, there are two possible classes of rank two square-zero supercharges.  The corresponding twisted theories are obtained by dimensionally reducing the 4d $\mc N=2$ theory twisted by a rank $(1,1)$, or a rank $(2,0)$ square-zero supercharge.  Let's first discuss the rank 1 twist, and its deformation to a perturbatively trivial rank 2 twist.

\begin{theorem} \label{3d_4_holo_A_twist_thm}
The minimal twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(\CC \times \RR_{\mr{dR}}, T^*[1](U/\!/\gg))$. The deformation of this theory to the rank 2 A-twist corresponds to deforming this theory to the 1-parameter family $\mr{Map}(\CC \times \RR_{\mr{dR}}, (U/\!/\gg)_{\mr{Hod}})$.
\end{theorem}

\begin{proof}
To prove this, we start with the one-parameter family of 4d twisted theories which we computed Theorem \ref{4d_Donaldson_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to reduce to a one-parameter family of 3d twisted theories.
\end{proof}

\begin{theorem} \label{3d_2_B_twist_thm}
The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(\RR^3_{\mr{dR}}, U/\!/\gg)$.  This theory is generally only $\ZZ/2\ZZ$-graded.
\end{theorem}

\begin{proof}
Again, we prove this by dimensional reduction from a 4d $\mc N=2$ twisted theory, in this case the rank $(1,1)$ twist from Theorem \ref{4d_11_twist_thm}, by applying Proposition \ref{CS_diml_red_prop}.
\end{proof}
